---
name: Ana Bravo
#surname: Bravo
position: "Data Analyst"
address: "Miami, Florida"
#phone: +1 22 3333 4444
www: anbrav0.github.io
email: "anbravo@fiu.edu"
#twitter: mariecurie
github: anbrav0
aboutme: Specialized in cleaning, analyzing, interpreting, and visualizing data using R programming.  
linkedin: anabravobiostats
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(readxl)
library(here)
library(kableExtra)
```

```{r function}
# install.packages("readxl") uncomment this if you need to install the package

readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
  

}
```


```{r load-excel, include=FALSE}
filename <- here::here("ana_bravo_vitae_cv", 
                       "Bravo_vitae_data.xlsx")

readExcelSheets(filename)

#readExcelSheets(here::here("Bravo_vitae_data.xlsx"))
```


# Education

```{r}
library(tibble)
education %>% 
  detailed_entries( what = degree,
                    when = year,
                    with = institution,
                    where = where,
                    why = details,
                    .protect = FALSE
    
  )
```

# Research Experience 

```{r}
research %>% 
  detailed_entries(
    what = role,
    when = dates,
    with = institution,
    where = where,
    why = details,
    .protect = FALSE
    
  )
```

# Professional Experience 

```{r professional-experience-table, include=FALSE, results='asis'}

Professional_experience <- tribble(
  ~title, ~department, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~details,
  
  "Lab Instructor",
  "Mathematics Department",
  "Febuary",
  2019,
  "October",
  2020,
  "Miami Dade College",
  "Serve as a role model to motivate students to achieve their academic needs. 
  \\begin{itemize}
     \\item Advisement service.
     \\item SMART Plan creation.
     \\item Advising appointments.
     \\item Meeting with students on repeated attempts.
     \\item Assist with enrollment. 
     \\item Create, review, and modify student academic progress (MAP) for newly enrolled, transfer and transient students. 
     \\item Assist students with academic planners such as major changes and pre-requisit requirements. 
     \\item Participate in recruitment services such as orientation for First time in College (FTIC) students 
     \\item Advise and guide students who were on academic probation to implement alternative courses of action to achieve graudation. 
  \\end{itemize}",
  
  "Mathematics Tutor", 
  "Mathematics Department",
  "October",
  2016, 
  "January",
  2019, 
  "Miami Dade College",
  "Provide homework help, assist in the creation of study plans, and develop an in-depth knowledge in College Mathematics.
  \\begin{itemize}
     \\item Attend instructor meetings or requires yearly training for online courses.
     \\item Grade and score day one diagnostics exam to identify students current mathematics background
     \\item Help in the Navigation of online modalities for students such as ALEKS, myMathLab, and BlackBoard
     \\item Create study plan for students identified as at risk based on students day one diagnostics exam. 
     \\item Monitor online BlackBoard Retention Center and communicate weekly with professor.
     \\item Conduct Mastery sessions (e.g., review sessions) during tutoring service hours in preparation for exam week.
  \\end{itemize}"
  )

```


```{r profession-experience, results='asis'}
Professional_experience %>% 
  detailed_entries(
    with = title,
    what = department,
    why = details,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}", .na = ""),
    where = where,
    .protect = FALSE
  )

```

# Language Skills 

```{r skills-tribble, include=FALSE}

#skills_tribble <- tribble(
  #~Programming, ~Software,
  #"R",    "Github",
  #"Rstudio", "COVID-19 Project",
  #"RMarkdown", "LateX",
  #"SAS", "SAS on Demand"
#)

```


```{r, include=FALSE}
#skills_tribble %>% 
 # kbl() %>% 
  #kable_classic_2(full_width = FALSE)
```

```{r skills}
`skills ` %>% 
  kable(booktabs = TRUE, format = "latex") %>% 
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>% 
  column_spec(3, width = "27em")

```

# Leadership, Service & Community Engagement  

```{r community-tribble, include=FALSE}

community_tribble <- tribble(
  ~title, ~department, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~details,
  
  "Rentetion Data Core - ABCD Student Rention Workgroup",
  "ABCD Study",
  "April",
  2023,
  "April",
  2024, 
  "ABCD Study Consortium",
  "Retention Core Member
  \\begin{itemize}
    \\item Assist in the creation of retention efforts ABCD model for at risk participants.
    \\item Create, clean, and model passive withdraw participatants as well as identify participants at risk of study withdrawl.
   \\end{itemize}",
  
  "Dean Student Advisory Biostatistics Respresentative",
  "Robert Stempel College of Public Health and Social Work",
  "August",
  2022,
  "August",
  2023, 
  "Office of Student and Alumni Affairs",
  "Advisor Council Board Memeber
  \\begin{itemize}
    \\item Biostatistics Department representative, make recommendation for improvement of departmental needs.
    \\item Provide knoweldge for key decision making in Biostatistics department.
  \\end{itemize}",
  
  
  "Data Science Conference 2022 Volunteer",
  "DSC US Health 22",
  "October",
  2022,
  "October",
  2022,
  "FIU Kovens Conference Center",
  "Data Science conference Volunteer
  \\begin{itemize}
    \\item Assist with logist front desk task such as check in, organization of materials.
    \\item Advise DSC attendees location of important events.
  \\end{itemize}",
  
  
  "ABCD Study Substance Use Workgroup Member",
  "ABCD Study",
  "June",
  2021,
  "April",
  2023,
  "ABCD Consortium",
  "Research Assistant trainee input
  \\begin{itemize}
    \\item Provide localized insight on the RA groudfloor for the ABCD Study.
    \\item Provide assistance in reformatting script language for the ABCD Semi-structured TLFB interview.
  \\end{itemize}",
  
  "The Childrens Trust Expo Recruitment",
  "Child Anxiety and Phobia Lab",
  "September",
  2018,
  "September",
  2018,
  "MDC Wolfson Campus",
  "Recruitor for EMU study and Child Anxiety and Phobia Program.
  \\begin{itemize}
    \\item Offer resources to families to participate in sleep study and anxiety and treatment services at FIU.
    \\item Recruit for EMU study, a sleep study interested in looking at sleep and anxiety using MRI facilities.
  \\end{itemize}",
  
  "Open House and Parent Resource provider",
  "Child Anxiety and Phobia Lab",
  "September",
  2019,
  "September",
  2019,
  "Miami Heights Elementary",
  "Outreach Program Efforts.
  \\begin{itemize}
    \\item Parent resource night outreach program to school age children and parents interested in treatment services.
    \\item Offer CCF resources to parents available in the South Florida Area.
  \\end{itemize}"
)

```


```{r community-engagement}
community_tribble %>% 
  detailed_entries(
    with = title,
    what = department,
    why = details,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}", .na = ""),
    where = where,
    .protect = FALSE
  )
```


# Publications

```{r include=FALSE}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

Yeguez, C.E., **Bravo, A.,** Troya, S., Pettit, J.W., (In preparation). Are Individuals with ADHD at Risk for Suicide? A Systematic Review of Longitudinal Studies. 

**Bravo, A.,** Wang, W., Rojas, P., (In preparation). Examining Sociocultural Factors of Hispanic Stress: A Community Based Repeated Measures Study in South Florida among Latinx Adolescents.

